Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-08-31 doc/paper.tex
LS pseudocode: error fix
LS pseudocode: completed
pseudocode update
dopunjen LS
hyrid added

      Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$. Afterwords, for each $p_i$ which are dropped off, we take the guard which is nearest by distance from $p_i$ and add them into $s^p$. 
     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK? } as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$. 
       	  \item \emph{topological-type benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price. 
       	  \item    ...
       \end{itemize}
     \section{Conclusions and Future Work}

>>>>

      Another criterion for the neighbourhood's configuration ($k$-th) would be taking arbitrary $k$ guards $\{p_1,...,p_d\}$ from $s^p$, then drop them from $s^p$. Afterwords, for each $p_i$ which are dropped off, we take the guard which is the nearest by distance from $p_i$ and add them into $s^p$.

      \subsection{Hybrid of the Greed Heuristic and Local Search}

       In order to improve the results of the Greedy heuristic, we propose a hybridization with the LS method. 
       The pseudocode is given in Algorithm~\ref{alg: hybrid-ls-greedy}.
        \begin{algorithm}[!t]
       	\caption{Local Search}\label{alg:hybrid-ls-greedy}
       	\begin{algorithmic}
       		   	\State \textbf{Input:} and Instance of the problem; $pct$:percentage
       		    \State \textbf{Output:} a complete solution $s$
       		    \State $s_{greedy} \gets \emptyset$
       		    \While{ $s_{greedy}$ is not complete}
       		        \State $s^P \gets$ call Greedy to expend $s_{greedy}$ for (up to) $\lfloor n \cdot p \rfloor$ guards 
       		        \State $s_{greedy} \gets$ LS($s^P$)
       		    \EndWhile
       \end{algorithmic}
       \end{algorithm}

       \begin{algorithm}[!t]
      	\caption{Local Search}\label{alg:local-search}
      	\begin{algorithmic}[1]
      		\State \textbf{Input:} a (partial) solution $s_{greedy}=\{v_1,...,v_k\}$, $iter_{allow}>0., $ probability $p$ 
      		\State \textbf{Output:} and improved solution $s$
      		\While{$iter < iter_{allow}$}
      		     \State $D(P)_s$ the number of points covered by $s_{greedy}$
      		      \If{$|D(P)_s| == |D(P)|$} // a complete solution
      		          \State return $s_{greedy}$
      		      \EndIf
      		     \State choose random vertex $v_{i'}$ from $s_{greedy}$
      		     \State $v_{i''},v_{i'''} \gets$ two neighbor vertices of vertex  $v_{i'}$
      		     \State $s^1_{greedy} \gets$ $s_{greedy} \cup \{v_{i''} \} \setminus \{v_{i'}\}$
                 \State $s^2_{greedy} \gets$ $s_{greedy} \cup \{v_{i'''} \} \setminus \{v_{i'}\}$
      		      \If{$|D(P)_{s^1_{greedy}}|>|D(P)_{s_{greedy}}|$ }
                        \State $s_{greedy} \gets s^1_{greedy}$
      \EndIf
                    \If {$|D(P)_{s^1_{greedy}}|==|D(P)_{s_{greedy}}|$ }
                        \State $s_{greedy} \gets s^1_{greedy}$ with probability $p$

      		      \EndIf     
      		       \If{$|D(P)_{s^2_{greedy}}|>|D(P)_{s_{greedy}}|$ }
                        \State $s_{greedy} \gets s^2_{greedy}$
      		      \EndIf

            \If {$|D(P)_{s^2_{greedy}}|==|D(P)_{s_{greedy}}|$ }
                        \State $s_{greedy} \gets s^2_{greedy}$ with probability $p$
                    \EndIf
      		     \State $iter \gets iter +1 $
      		\EndWhile
      		 \State return $s_{greedy}$
      	\end{algorithmic}
      \end{algorithm}

     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK? } as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
       	  \item \emph{topological-type benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	  \item    ...
       \end{itemize}
     \section{Conclusions and Future Work}
